Revisiting Multi-Domain Machine Translation

### 2020-05-04 2020/coling2020/multidomain.tex
10 pages limits, last results are almost there

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.
\newcommand{\fyTodo}[1]{\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyTodostar}[1]{\Todo*[FY:]{\textcolor{orange}{#1}}
\newcommand{\fyDone}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyFuture}[1]{\done[FY]\Todo[FY:]{\textcolor{red}{#1}}}
\newcommand{\fyDonestar}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\jcTodo}[1]{\Todo[JC:]{\textcolor{blue}{#1}}}
\newcommand{\jcDone}[1]{\done[JC]\Todo[JC:]{\textcolor{blue}{#1}}}

\newcommand{\src}{\ensuremath{\mathbf{f}}} % source sentence
\newcommand{\trg}{\ensuremath{\mathbf{e}}} % target sentence
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{\textbf{#1}}}
\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
\newcommand{\SB}[1]{\textcolor{green}{#1}}
\newcommand{\SW}[1]{\textcolor{red}{#1}}

@@

In this paper, we formulate in a more precise fashion the requirements that an effective MDMT system should meet (section~\ref{sec:requirements}). Our first contribution is thus of methodological nature and consists of lists of expected properties of MDMT system and associated measurements to evaluate them (section~\ref{sec:challenging}). In doing so, we also shed lights on new problems that arise in this context, regarding for instance the accomodation of new domains in the course of training, or the computation of automating domain tags.\fyDone{New problems - continuous learning, automatic domains} Our second main contribution is experimental and consists in a thorough reanalysis of eight recent multi-domain approaches from the literature, including a variant of a model initially introduced for DA. We show in section~\ref{sec:experiments}  existing approaches still fall short to match many of these requirements, notably with respect to handling a large amount of heterogeneous domains and to dynamically integrating new domains in training.\fyDone{Spell out conclusions}

@@

Combining multiple domain-specific MTs can also be justified in the sake of distributional robustness \cite{Mansour09domainadaptation,Mansour09multiple}, for instance when the test mixture differs from the train mixture, or when it includes new domains unseen in training. Such scenario is already well documented for zero-shot multi-lingual MT \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual}, where mixing languages has more than demonstrated its usefulness.  An even more challenging case is when the MT would need to perform well for any test distribution (as studied for statistical MT in \cite{Huck15mixeddomain}). In all these cases, mixing domains in training and/or testing is likely to improve robustness against unexpected or adversarial inputs \cite{Oren19distributionally}.

@@

\paragraph{[P3-HET]}
The notion of a domain being a fragile one, an effective MDMT system should be able to discover not only when cross-domain sharing is useful (cf.\ requirement [P2-TUN])\jcDone{what is P2.2?}, but also when intra-domain heterogeneity is hurting. This requirement is tested by artificially conjoining two separate domains into one during training. The loss in performance with respect to the baseline (using correct domain tags) should then be as small as possible.

\paragraph{[P4-ERR]}
A MDMT should perform best when the true domain tag is known, but deteriorate gracefully in the presence of domain tag errors. This is in sharp contrast with what is observed with fine-tuning, where using the wrong domain tag can yield ``catastrophic'' drops in performance. This requirement can be measured by translating test texts for domain $A$ with all erroneous or random domain tags and measure the correlated decrease in performance.

\paragraph{[P5-UNK]}
A related situation occurs when the domain of a test document is unknown. Several situations need be considered: when the domain is seen in training, then using automatically predicted domain labels should not be much worse than using the correct one. This procedure can also be used test documents from unknown domains (zero-shot transfer). A good MD system should there outperform the default baseline that merges all available data.\fyDone{Systems react to unknown domains}
% These requirements are respectively labelled [P5.1] and [P5.2]\fyTodo{Not so sure of these ones}.

\paragraph{[P6-DYN]}
Another requirement, more of an operational nature, is that a MDMT system should smoothly evolve to accomodate a growing number of domains, without having to retrain the full system each time new data is available. This is a requirement [P6-DYN] that we challenge by dynamically changing the number of training and test domains.

@@

\begin{itemize}
\item a generic model trained on a concatenation of all corpora (\texttt{Mixed}). We develop two versions of this system, one where domain unbalance reflects the distribution of our parallel data (\system{Mixed-Nat}) and one where all domains are equally represented in training (\system{Mixed-Bal}). The former is the best option when the train mixture $\mathcal{D}^s$ is also observed in testing; the latter should be used when the test distribution is uniform across domains. Accordingly, we report two aggrate scores: a weighted average reflecting the default distribution, and an unweighted average (test domains are equally important).
%   As explained above, depending whether MDMT are expected to perform specially well on large domains, or to treat all domains equally, one or the other training distribution should be prefered.\jcDone{All systems cand be learned following both Bal and Nat. does Nat corresponds to wAVG in test? is wAVG defined somewhere?}
\item fine-tuned models \cite{Luong15stanford,Freitag16fast}\jcDone{i would use Luong and Manning 2015}, based on the \system{Mixed-Nat} system, further trained on each domain for at most 20~000 iterations, with early stopping when the dev BLEU stops increasing. We again contrast two versions: full fine-tuning (\system{FT-Full}), which may update all the parameters of the initial generic model; and the variant of \cite{Bapna19simple}, where fine-tuning only updates a simple adaptation module that is added (with residual connexions) on top of every Transformer layer (\system{FT-Block}).
\end{itemize}

For all models, we set the embeddings size and the hidden layers size to~512. Transformers use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. The multi-domain residual system (see description below) additionally use an adaptation block in each transformer layer, composed of 2-layer perceptron, with an inner RELU activation function operating on normalized entries of dimension 1024. The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
 %
Training use a batch size of~128; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.\fyDone{Describe the block adaptation layer - voir slides} 
 % All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.
\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes the following reimplementations of recent proposals from the literature:
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or introduced in the form of a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDC-Feat});
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \cite{Zeng18multidomain} (\system{WDCMT}): in this approach, two representations, a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification models and adversarial training are used to compute these representations.\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly, improved results.}\fyTodo{Check this}
\item an original, multi-domain, version of the approach of \newcite{Bapna19simple}, denoted \system{MDL Res}, where a domain-specific adaptation module is included in all the Transformer layers; within each layer, residual connexions make it possible to by-pass this module.
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
Contrarily to \cite{Bapna19simple}, we do not start with a trained generic system, but learn the multi-domain from scratch.\fyDone{Check this.}
\end{itemize}

@@

In this study, all systems fail to outperform fine-tuning, sometimes by a wide margin, as is the case for an ``isolated'' domain such as \domain{rel}. This might be expected, since all domains are well separated (cf.\ Section~\ref{ssec:corpora}) and are hardly helping each other. In this situation, MDMT systems should make sure that each domain is allocated a sufficient number of specific parameters, so as to close the gap with fine-tuning.
\fyDone{More comments when we have all the results}\fyDone{Importance of sharing and unsharing}
36.81	53.85	47.21	30	35.74	60.24	39.2	44.0	21.06
\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}|} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c||}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Rnn}  & 36.81 & 53.85 & 47.21 & 30 & 35.74 & 60.24  & 39.2  & 44.0 \\
    \system{Mixed-Bal}   &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.7 & 53.8\\
   \system{FT-Block}     & 37.3 & \SB{57.9} & 53.9 & 33.8 & \SB{46.7} & \SB{90.2}  & 42.3 & 53.3 \\ \hline % & 20.5\\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.6 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat}      & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDC-Tag}     & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} &40.9 & 49.8          \\% & 22.1 \\ 
    \system{TTM}            & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.0 & 49.7     \\% &  23.4 \\
    \system{DM}             & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 38.1 & 43.4 \\ % & 22.6\\
    \system{ADM}           & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 38.9 & 47.5 \\% & 23.3 \\
    \system{WDCMT}       & 35.96 & 53.31 & 48.83 & 31.15 & 38.81 & 58.52 & 39.0 & 44.4 \\ % & 20.4 \\
    \system{MDL Res}     & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.0 & 51.9 \\%  & \SW{21.2} \\
    \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems. We report the BLEU score for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. Boldface denotes significant differences with respect to the \system{Mix-Nat} system.}
  \label{tab:performance}
  \fyTodo{Fill the table with all results, including a comparison with *RNNs* for wcmd}
  \fyTodo{Do we have significancy tests for averages?}
  \fyTodo{Add tests wrt to RNN}
\end{table*}

@@

Table~\ref{tab:redomains} summaries the results of four experiments where we artificially redefine the boundaries of domains, with the aim to challenge requirements [P2-TUN], [P3-HET], and [P4-ERR]. In first three, we randomly \emph{split} one corpus in two parts and proceed as if this corresponded to two actual domains. A MD system should detect that these two pseudo-domains should be mutually beneficial, and should be hardly affected by this change with respect to the baseline scenario (no split). In this situation, we should expect MDMT to even surpass fine-tuning separately on each of these dummy domain, as MDMT exploits all data, where fine-tuning focuses only on a subpart. In testing, we decode the test set twice, once with each pseudo-domain tag. This makes no difference for \system{TMM}, \system{ADM}, \system{ADM} and \system{WDCMT}, which do not use domain tags in testing.
In the \textsl{merge} experiment, we do the reverse and merge two corpora in training, in order to assess the robustness with respect to heterogenous domains. We then translate the two corresponding test sets with the same (merged) system.

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{old} &  \multicolumn{1}{c|}{new}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_1$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5}& -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& 32.55 & \SW{-3.28}\\
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}$^+$& +0.2& -2.2 & -2.9 & -0.5 & -0.4 & 35.92 & \SW{-1.7}\\
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3} $^+$ & +0.3 & +0.3 & +0.3 & 0.3 & +0.1 & 34.91 &\SW{-1.8}\\
    \system{LDC-Tag}   & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& 37.01 & \SW{-1.4}\\ 
    \system{TTM} (!)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (!)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & &-0.9\\
    \system{ADM} (!)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & &-0.2\\
    \system{WDCMT} (!)     & -0.03    & -0.03  & +0.2 & +0.2  & +0.83 & +0.83  & -0.45 & -0.85 & *** & 0.19 \\
    \system{MDL Res}   & -0.2   & -0.07 & +\SB{0.18}$^+$ &+0.0 & -0.89 & -0.89 & +\SB{0.7} & -0.35 & 31.78 & \SW{-1.3}\\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. For the Split experiments, we only report the loss in performance for the concerned test set (\domain{med} or \domain{law}), (*) denote significant losses when domains are split or merged; (+) denotes a significant improvement over \system{Full FT}; \fyTodo{Check significance}\fyTodo{How about wrong ?}}
  \label{tab:redomains}
\end{table*}

>>>>

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.
\newcommand{\fyTodo}[1]{\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyTodostar}[1]{\Todo*[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyDone}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyFuture}[1]{\done[FY]\Todo[FY:]{\textcolor{red}{#1}}}
\newcommand{\fyDonestar}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\jcTodo}[1]{\Todo[JC:]{\textcolor{blue}{#1}}}
\newcommand{\jcDone}[1]{\done[JC]\Todo[JC:]{\textcolor{blue}{#1}}}

\newcommand{\src}{\ensuremath{\mathbf{f}}} % source sentence
\newcommand{\trg}{\ensuremath{\mathbf{e}}} % target sentence
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{\textbf{#1}}}
\newcommand{\vlambda}{\ensuremath{\boldsymbol\lambda}\xspace} % parameters vector for a distribution
\newcommand{\indic}[1]{\ensuremath{\mathbb{I}(#1)}}
% \newcommand{\SB}[1]{\textcolor{green}{#1}}
% \newcommand{\SW}[1]{\textcolor{red}{#1}}
\newcommand{\SB}[1]{\textbf{#1}}
\newcommand{\SW}[1]{\underline{#1}}
\renewcommand\textfraction{.1}
\renewcommand\floatpagefraction{.95}

@@

In this paper, we formulate in a more precise fashion the requirements that an effective MDMT system should meet (section~\ref{sec:requirements}). Our first contribution is thus of methodological nature and consists of lists of expected properties of MDMT system and associated measurements to evaluate them (section~\ref{sec:challenging}). In doing so, we also shed lights on new problems that arise in this context, regarding for instance the accomodation of new domains in the course of training, or the computation of automating domain tags.\fyDone{New problems - continuous learning, automatic domains} Our second main contribution is experimental and consists in a thorough reanalysis of eight recent multi-domain approaches from the literature, including a variant of a model initially introduced for DA. We show in in Section~\ref{sec:experiments} that existing approaches still fall short to match many of these requirements, notably with respect to handling a large amount of heterogeneous domains and to dynamically integrating new domains in training.\fyDone{Spell out conclusions}

@@

Combining multiple domain-specific MTs can also be justified in the sake of distributional robustness \cite{Mansour09domainadaptation,Mansour09multiple}, for instance when the test mixture differs from the train mixture, or when it includes new domains unseen in training. Such scenario is already well documented for zero-shot multilingual MT \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual}, where mixing languages has more than demonstrated its usefulness.  An even more challenging case is when the MT would need to perform well for any test distribution (as studied for statistical MT in \cite{Huck15mixeddomain}). In all these cases, mixing domains in training and/or testing is likely to improve robustness against unexpected or adversarial inputs \cite{Oren19distributionally}.

@@

\paragraph{[P3-HET]}
The notion of a domain being a fragile one, an effective MDMT system should be able to discover not only when cross-domain sharing is useful (cf.\ requirement [P2-TUN])\jcDone{what is P2.2?}, but also when intra-domain heterogeneity is hurting. This requirement is tested by artificially conjoining separate domains into one during training, hoping that the loss in performance with respect to the baseline (using correct domain tags) will remain small.

\paragraph{[P4-ERR]}
A MDMT should perform best when the true domain tag is known, but deteriorate gracefully in the presence of tag errors; in this situation, it has been observed that could yield ``catastrophic'' drops in performance. This requirement can be measured by translating test texts for domain $A$ with erroneous or random domain tags and measure the correlated loss.

\paragraph{[P5-UNK]}
A related situation occurs when the domain of a test document is unknown. Several situations need be considered: for domain is seen in training, then using automatically predicted domain labels should not be much worse than using the correct one. For test documents from unknown domains (zero-shot transfer), a good MD system should ideally outperform the default baseline that merges all available data.\fyDone{Systems react to unknown domains}
% These requirements are respectively labelled [P5.1] and [P5.2]\fyTodo{Not so sure of these ones}.

\paragraph{[P6-DYN]}
Another requirement, more of an operational nature, is that a MDMT system should smoothly evolve to handle a growing number of domains, without having to retrain the full system each time new data is available. This is a requirement [P6-DYN] that we challenge by dynamically changing the number of training and test domains.

@@

\begin{itemize}
\item a generic model trained on a concatenation of all corpora (\texttt{Mixed}). We develop two versions\footnote{In fact three: to enable a fair comparison with WDCMT, a RNN-based variant is also trained and evaluated.} of this system, one where domain unbalance reflects the distribution of our parallel data (\system{Mixed-Nat}) and one where all domains are equally represented in training (\system{Mixed-Bal}). The former is the best option when the train mixture $\mathcal{D}^s$ is also observed in testing; the latter should be used when the test distribution is uniform across domains. Accordingly, we report two aggregate scores: a weighted average reflecting the default distribution, and an unweighted average, meaning that test domains are equally important.
%   As explained above, depending whether MDMT are expected to perform specially well on large domains, or to treat all domains equally, one or the other training distribution should be prefered.\jcDone{All systems cand be learned following both Bal and Nat. does Nat corresponds to wAVG in test? is wAVG defined somewhere?}
\item fine-tuned models \cite{Luong15stanford,Freitag16fast}\jcDone{i would use Luong and Manning 2015}, based on the \system{Mixed-Nat} system, further trained on each domain for at most 20~000 iterations, with early stopping when the dev BLEU stops increasing. We again contrast two versions: full fine-tuning (\system{FT-Full}), which may update all the parameters of the initial generic model; and the variant of \cite{Bapna19simple}, where fine-tuning only updates a simple adaptation module that is added (with residual connexions) on top of every Transformer layer (\system{FT-Block}).
\end{itemize}

For all models, we set the embeddings size and the hidden layers size to~512. Transformers use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. The multi-domain residual system (see description below) additionally use an adaptation block in each transformer layer, composed of 2-layer perceptron, with an inner RELU activation function operating on normalized entries of dimension 1024. The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
 %
Training use a batch size of~128; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.\fyDone{Describe the block adaptation layer - voir slides} 
 % All our systems are implemented in OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein17opennmt}.
\subsection{Multi-domain systems \label{ssec:systems}}
\fyDone{Remove Gated residual}
Our comparison of multi-domain systems includes the following reimplementations of recent proposals from the literature:
\begin{itemize}
\item a system using domain control as in \cite{Kobus17domaincontrol}: domain information is introduced either as an additional token for each source sentence (\system{DC-Tag}), or introduced in the form of a supplementary feature for each word (\system{DC-Feat}).
\item a system using lexicalized domain representations \cite{Pham19generic}: word embeddings are composed of a generic and a domain specific part (\system{LDC-Feat});
\item the three proposals of \newcite{Britz17mixing}. \system{TTM} is a feature-based approach where the domain tag is introduced as an extra word \textsl{on the target side}. Training uses reference tags and inference is performed with predicted tags, just like for regular target words. \system{DM} is a multi-task learner where a domain classifier is trained on top the MT encoder, so as to make it aware of domain differences; \system{ADM} is the adversarial version of \system{DM}, pushing the encoder towards learning domain-independent source representations. These methods thus only use domain tags in training.
\item the multi-domain model of \newcite{Zeng18multidomain} (\system{WDCMT}), where a domain-agnostic and a domain-specialized representation of the input are simultaneously processed; supervised classification and adversarial training are used to compute these representations.\footnote{For this system, we use the available RNN-based system from the authors (\url{https://github.com/DeepLearnXMU/WDCNMT}\fyDone{URLs}) which does not directly compare to the other, Transformer-based, systems; the improved version of \cite{Su19exploring} seems to produce comparable, albeit slightly, improved results.}\fyDone{Check this}
\item an original, multi-domain, version of the approach of \newcite{Bapna19simple}, denoted \system{MDL Res}, where a domain-specific adaptation module is included in all the Transformer layers; within each layer, residual connexions make it possible to by-pass this module.
  % In a variant (\system{MDL Gated}), we use a gating mechanism to merge computations using the the adapter modules and with those that don not.
Contrarily to \cite{Bapna19simple}, we do not start with a trained generic system, but learn the multi-domain from scratch.\fyDone{Check this.}
\end{itemize}

@@

All systems fail to outperform fine-tuning, sometimes by a wide margin, especially for an ``isolated'' domain like \domain{rel}. This might be due to the fact that domains are well separated (cf.\ Section~\ref{ssec:corpora}) and are hardly helping each other. In this situation, MDMT systems should instead make sure that each domain is allocated a sufficient number of parameters, so as to close the gap with fine-tuning.
\fyDone{More comments when we have all the results}\fyDone{Importance of sharing and unsharing}
% 36.81	53.85	47.21	30	35.74	60.24	39.2	44.0	21.06
\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Mixed-Nat-RNN}  & 36.8 & 53.8 & 47.2 & 30.0 & 35.7 & 60.2  & 39.2  & 44.0 \\
    \system{Mixed-Bal}   &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.7 & 53.8\\
   \system{FT-Block}     & 37.3 & \SB{57.9} & 53.9 & 33.8 & \SB{46.7} & \SB{90.2}  & 42.3 & 53.3 \\ \hline % & 20.5\\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.6 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat}      & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDC-Tag}     & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} &40.9 & 49.8          \\% & 22.1 \\ 
    \system{TTM}            & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.0 & 49.7     \\% &  23.4 \\
    \system{DM}             & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 38.1 & 43.4 \\ % & 22.6\\
    \system{ADM}           & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 38.9 & 47.5 \\% & 23.3 \\
    \system{WDCMT}       & 36.0 & 53.3 & 48.8 & 31.1 & 38.8 & 58.5 & 39.0 & 44.4 \\ % & 20.4 \\
    \system{MDL Res}     & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.0 & 51.9 \\%  & \SW{21.2} \\
    \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems. We report BLEU scores for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. Boldface denotes significant gains with respect to \system{Mix-Nat}, underline denotes significant losses.}
  \label{tab:performance}
%  \fyDone{Fill the table with all results, including a comparison with *RNNs* for wcmd}\fyTodo{Do we have significancy tests for averages?} \fyTodo{Add tests wrt to RNN}
\end{table*}

@@

Table~\ref{tab:redomains} summaries the results of four experiments where we artificially redefine the boundaries of domains, with the aim to challenge requirements [P2-TUN], [P3-HET], and [P4-ERR]. In first three, we randomly \emph{split} one corpus in two parts and proceed as if this corresponded to two actual domains. A MD system should detect that these two pseudo-domains should be mutually beneficial, and should be hardly affected by this change with respect to the baseline scenario (no split). In this situation, we should expect MDMT to even surpass fine-tuning separately on each of these dummy domains, as MDMT exploits all data, while fine-tuning focuses only on a subpart. In testing, we decode the test set twice, once with each pseudo-domain tag. This makes no difference for \system{TMM}, \system{ADM}, \system{ADM} and \system{WDCMT}, which do not use domain tags in testing.
In the \textsl{merge} experiment, we merge two corpora in training, in order to assess the robustness with respect to heterogenous domains [P3-HET]. We then translate the two corresponding tests with the same system.

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{old} &  \multicolumn{1}{c|}{new}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_1$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5} & -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& 32.55 & \SW{-3.3}\\
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}  & +0.2& -2.2 & -2.9 & -0.5 & -0.4 & 35.92 & \SW{-1.7}\\
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3}   & +0.3 & +0.3 & +0.3 & 0.3 & +0.1 & 34.91 &\SW{-1.8}\\
    \system{LDC-Tag}   & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& 37.01 & \SW{-1.4}\\ 
    \system{TTM} (*)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & 0.0 & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (*)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & 0.0 &-0.9\\
    \system{ADM} (*)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & 0.0&-0.2\\
    \system{WDCMT} (*)     & -0.0    & -0.0  & +0.2 & +0.2  & +0.8 & +0.8  & -0.4 & -0.8 & 0.0 & +0.2 \\
    \system{MDL Res}   & -0.2   & -0.1 & +\SB{0.2} &+0.0 & -0.9 & -0.9 & +\SB{0.7} & -0.3 & 31.8 & \SW{-1.3}\\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. In the Split/Merge experiments, we report the loss in performance for the concerned test set(s). Underline denotes significant loss when domains are changed, bold a significant improvement over \system{Full FT}; (*) flags systems that ignore domain tags in testing.
    % \fyTodo{Check wrong and significance of diff}\fyDone{How about wrong ?}
  }
  \label{tab:redomains}
\end{table*}
